%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
%\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-red}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
\definecolor{darktext}{HTML}{000000}
\definecolor{text}{HTML}{000000}
\definecolor{graytext}{HTML}{000000}
\definecolor{lighttext}{HTML}{000000}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
%\photo[circle,noedge,left]{./examples/profile}
\name{Jose Nahuel}{Freitas}
\position{PhD in Physics. Researcher.}

\mobile{(+352) 661035384}
\email{nahuel.freitas@gmail.com}
%\homepage{www.posquit0.com}
\github{nfreitas}
\linkedin{nahuel-freitas}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \extrainfo{extra informations}

%\quote{``Be the change that you want to see in the world."}


%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {Satellogic.}
  {Scalabrini Ortiz 3333 3rd Floor \\ Buenos Aires \\ Argentina}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{General Application\\}
% How the letter is opened
\letteropening{}
\letteropening{\\Dear Satellogic recruiter,}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
%\letterenclosure[Attached]{Curriculum Vitae}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[R]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
  {Jose Nahuel Freitas~~~·~~~Cover Letter}
  {}

% Print the title with above letter informations
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}
  It is my pleasure to contact you to inquire about available positions within
  Satellogic. I am an experienced academic researcher and I am now looking for new
  horizons in the productive sector.

  I obtained a PhD in Physics at the University of Buenos Aires in 2017, during which I focused on basic theoretical
  aspects of quantum and statistical physics, while I also explored more general
  interests by taking courses on neuroscience, artificial intelligence, and synthetic
  biology. In recent years I turned to a more applied line of research related to
  the energetics of electronic circuits and new information processing paradigms
  like probabilistic computing. I also had ample experience working in research
  labs, designing electronic circuits, and developing software.

  As part of my academic career, I had the opportunity to work in several countries
  and institutions, which allowed me to develop valuable skills related to team-working,
  teaching, and effective communication of scientific results. I am now holding a
  research position at the University of Luxembourg, although my intention is to return
  to Argentina in the medium term. At the same time, I would like to
  transition from the academic to the productive/technological sector. I am
  eager to apply my knowledge and skills to technological or scientific problems
  with a direct impact on society.

  For the above reasons, I find Satellogic as an ideal place to develop my new career
  path. I feel attracted by the ambitious goals of the company as well as the many
  interesting technological challenges that ensue. Also, it is an added value
  for me to be part of this endeavor in a developing country like Argentina. Having
  said that, I might also consider working for some time in one of the other countries in which the company is based, if required.

  Finally, I hope that a profile like mine would be of interest to Satellogic,
  and I look forward to your feedback.
  I am confident I could contribute to diverse tasks ranging from software development,
  data analysis and AI, to electronic and optical systems design.
  I can be contacted at any time at the email and phone number provided above.


\end{cvletter}


%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter informations
\makeletterclosing

\end{document}
