%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Postdoctoral researcher} % Job title
    %{University of Luxembourg (group of Prof. Massimiliano Esposito).} % Organization
    {University of Luxembourg} % Organization
    {Luxembourg} % Location
    {Oct. 2018 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Study of the energetics of information processing with electronic circuits from the
        point of view of modern stochastic thermodynamics.}
        \item {Design of experiments to test and study refrigeration cycles in electrical systems.}
        \item {Development of a long-term research plan and preparation of funding applications.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Short-term invited researcher} % Job title
    {University of Mainz} % Organization
    %{University of Mainz (group of Prof. Ferdinand Schmidt-Kaler) } % Organization
    {Mainz, Germany} % Location
    {Jun. 2018 - Oct. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Mathematical modeling of a high-precision experiment with trapped ions to study the thermodynamical
        limits to the measurement of time.
        \item Design of an efficient algorithm for the analysis of very long time series and clock stability.
        \item Assisted in the supervision of a master student.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Postdoctoral researcher} % Job title
    %{Saarland University (group of Prof. Giovanna Morigi) } % Organization
    {Saarland University} % Organization
    {Saarbrucken, Germany} % Location
    {Jun. 2017 - Apr. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Application of machine learning techniques for the computational
        description and manipulation of many-body quantum states.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Doctoral researcher} % Job title
    %{University of Buenos Aires (QUFIBA group) } % Organization
    {University of Buenos Aires} % Organization
    {Buenos Aires, Argentina} % Location
    {Apr. 2012 - Apr. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Identification of fundamental limits for cooling in a family of driven quantum refrigerators.
        \item Study of heat transport in harmonic lattices, in particual crystals of trapped ions.
        \item Quantum simulation of magnetic materials in ion traps. Quantum correlations and decoherence.
        \item Design of a genetic algorithm for the optimization of ion crystal structure.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Assistant teacher} % Job title
    {University of Buenos Aires, Physics department} % Organization
    {Buenos Aires, Argentina} % Location
    {Jun. 2009 - Jun. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Teaching of several theoretical and experimental subjects such as Classical, Quantum and Statistical Mechanics,
        Electromagnetism, Fluid Mechanics, and Experimental Techniques.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Undergraduate student} % Job title
    {Institute of Scientific and Technical Research for Defense (CITEDEF)} % Organization
    {Buenos Aires, Argentina} % Location
    {Apr. 2010 - Dec. 2010} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Development of a coincide detector with nanosecond resolution.
        \item Quantum optical experiments with correlated photons.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software developer} % Job title
    {Movilogic S.A.} % Organization
    {Buenos Aires, Argentina} % Location
    {Mar. 2004 - Mar. 2006} % Date(s)
    {
      \begin{cvitems}
        \item Mobile/Web developer of sales applications (for early handheld devices like the Palm Treo).
        \item Database management.
      \end{cvitems}
    }


  \cventry
    {Software developer} % Job title
    {Audiotel S.A.} % Organization
    {Buenos Aires, Argentina} % Location
    {Mar. 2003 - Mar. 2004} % Date(s)
    {
      \begin{cvitems}
        \item Programming of IVR (Interactive Voice Response) applications.
        \item Management of PBX telephone systems.
      \end{cvitems}
    }

\end{cventries}
